---
title: "PSY 8712 Week 8 Project"
author: "Amanda Jensen"
output: 
  html_document:
    df_print: paged
---

### Reproducible Image and Online Resources
An image of this project as of *`r format(Sys.Date(), '%B %d %Y')`* can be accessed by [clicking this link](https://hub.ovh2.mybinder.org/user/jens2482-psy8712-week8-71cbvnyk/lab).
An interactive web app is available by [clicking this link](https://hub.ovh2.mybinder.org/user/jens2482-psy8712-week8-71cbvnyk/lab) instead.

### Script Settings and Resources
```{r setup, warning = FALSE, message = FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

### Data Import and Cleaning
In this chunk, I cleaned the data using the same techniques we used in Week 7, I made sure all the variables had an appropriate class designation and changed reverse coded q5 by subtracting all values from 6. 
```{r data_import, warning = FALSE, message = FALSE}
week8_tbl <- read_csv ("../data/week3.csv") %>%
  mutate(timeStart = ymd_hms (timeStart)) %>%
  mutate(condition = factor(condition, 
                            levels = c("A", "B", "C"), 
                            labels = c("Block A", "Block B", "Control"))) %>%
  mutate(gender = factor(gender, 
                         levels = c("M", "F"), 
                         labels = c("Male", "Female"))) %>%
  mutate(q5 = 6 - q5)
```

