---
title: "PSY 8712 Week 8 Project"
author: "Amanda Jensen"
output: 
  html_document:
    df_print: paged
---

### Reproducible Image and Online Resources
An image of this project as of *`r format(Sys.Date(), '%B %d %Y')`* can be accessed by [clicking this link](https://hub.ovh2.mybinder.org/user/jens2482-psy8712-week8-71cbvnyk/lab).
An interactive web app is available by [clicking this link](http://jens2482.shinyapps.io/shiny_week8) instead.

### Script Settings and Resources
```{r setup, warning = FALSE, message = FALSE}
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

### Data Import and Cleaning
In this chunk, I cleaned the data using the same techniques we used in Week 7, I made sure all the variables had an appropriate class designation and changed reverse coded q5 by subtracting all values from 6. 
```{r data_import, warning = FALSE, message = FALSE}
week8_tbl <- read_csv ("../data/week3.csv") %>%
  mutate(timeStart = ymd_hms (timeStart)) %>%
  mutate(condition = factor(condition, 
                            levels = c("A", "B", "C"), 
                            labels = c("Block A", "Block B", "Control"))) %>%
  mutate(gender = factor(gender, 
                         levels = c("M", "F"), 
                         labels = c("Male", "Female"))) %>%
  mutate(q5 = 6 - q5)
```

### Visualization
This chunk creates a paginated table for questions 1-6, and I did this using brackets to select just those columns. For the scatterplot I compared the mean of the row for questions 1-6 to the mean of the row for questions 8-10.
```{r visualization, warning = FALSE, echo = FALSE, message = FALSE}

#table showing q1-16
week8_tbl[, c(paste0("q", 1:6))]

#scatterplot
week8_tbl %>%
  ggplot(aes(x = rowMeans(select(., q1:q6)), y = rowMeans(select(., q8:q10)))) +
  geom_point() +
  geom_smooth(method = "lm", color = "purple") +
  xlab("Mean Scores for Questions 1-6") +
  ylab("Mean Scores for Questions 8-10")
```

### Analysis
This chunk calculates the correlation and the corresponding p-value between means for questions 1-6 and questions 8-10.
```{r analysis, warning = FALSE, echo = FALSE, message = FALSE}
correlation <- cor.test(rowMeans(week8_tbl[, c(paste0("q", 1:6))]),
                        rowMeans(week8_tbl[, c(paste0("q", 8:10))]))

correlation
```
I observed a correlation of `r str_replace(formatC(correlation$estimate, format = "f", digits = 2), "^0", "")`. However, since the p-value associated with this correlation is not less than .05, it is not statistically significant.

### Data Export
This chunk exports the dataset as a CSV file.
```{r export, warning = FALSE, echo = FALSE, message = FALSE}
week8_tbl %>%
  write_csv("week8_tbl_simple.csv") # I am not sure what the simplified/skinny version means. I have a vague memory of you saying it once but I cannot find it in my notes anywhere.
```

